Inter-task effects lead to an unexpected bias in human computation

### 2014-07-19 docs/publications/2014.05_PNAS/figs.tex
add cross validation to classifier test
I have substancially changed how NBCAnalyzer works.  It uses proper
cross-validation (instead of random replicates, which has no
interpretable statistics).

In the course of doing this, I realized that pollution was hapenning in
my Naive Bayes Classifier -- the training set included the test set.
Correcting this obviously changed the results, actually in a good way.

I altered the plotting of classifier results -- both the
cross-comparison one and the longitudinal one.  In the cross-comparison
one, I added more pairwise comparisons, so now the comparison

\begin{figure}
	\includegraphics{figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

\begin{figure}
	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
	classifier.  The classifier is provided only the labels attributed to
	particular images as indicated on the abscissa.}
\end{figure}

>>>>

\begin{figure}
	\includegraphics{figs/f1-thetas_full_pairwise50_img1.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

\begin{figure}
	\includegraphics{figs/longitudinalF1scores-t0-t1_50.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
	$\textsc{cult}_{img}$ and $\textsc{ambg}$ using a Naive Bayes 
	classifier.  The classifier is provided only the labels attributed to
	particular images as indicated on the abscissa.}
\end{figure}

### 2014-07-19 docs/publications/2014.05_PNAS/manuscript.tex
add cross validation to classifier test
I have substancially changed how NBCAnalyzer works.  It uses proper
cross-validation (instead of random replicates, which has no
interpretable statistics).

In the course of doing this, I realized that pollution was hapenning in
my Naive Bayes Classifier -- the training set included the test set.
Correcting this obviously changed the results, actually in a good way.

I altered the plotting of classifier results -- both the
cross-comparison one and the longitudinal one.  In the cross-comparison
one, I added more pairwise comparisons, so now the comparison

\textbf{Statistical significance of $\theta_\text{NB}$.}
We test the significance two population's measured $\theta_\text{NB}$ against 
the null hypothesis that that the two populations are in fact identical:
\begin{align}
	\mathbf{H_0}: \theta_\text{NB} = 0 \\
	\mathbf{H_1}: \theta_\text{NB} > 0
\end{align}
If the populations are in fact identical, then the probability that the 
classifier correctly classifies a worker is $\frac{1}{2}$, and the probability 
of getting $k$ classifications during a cross-validation with $n$ 
test-classifications is:
\begin{align}
	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
\end{align}
Then, we have statistical significance if 
$\theta_\text{NB}$ is greater than a critical value, 
$\theta_\text{NB}^*$:
\begin{align}
	\theta_\text{NB} \geq 2k^* - 1
\end{align}
where $k^*$ is the minimum value required to satisfy
\begin{align}
	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
\end{align}
For a test-set of $n=40$ workers, and a significance of $\alpha = 0.05$, we
have $k^*=26 \implies \theta_\text{NB}^* = 0.65$.

>>>>

\textbf{Statistical significance of $\theta_\text{NB}$.}
We test the significance two population's measured $\theta_\text{NB}$ against 
the null hypothesis that that the two populations are in fact identical:
\begin{align}
	\mathbf{H_0}: \theta_\text{NB} = 0 \\
	\mathbf{H_1}: \theta_\text{NB} > 0
\end{align}
If the populations are in fact identical, then the probability that the 
classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
variable which denotes the number of correct classifications when the 
classifier is chalenged to classify a total of $n$ workers during 
cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
is:
\begin{align}
	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
\end{align}
We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
is greater than a critical value, $\theta_\text{NB}^*$:
\begin{align}
	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
\end{align}
where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
\begin{align}
	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
\end{align}
For a 5-fold cross-validation with non-overlapping test sets containing 25 
workers ($n = 125$), and a significance of $\alpha = 0.05$, we
have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.
